\Title

### 2021-05-28 manuscript/content.tex
Replace residue for residuals on manuscript

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix vs different window sizes. Each memory requirement corresponds
        to the ammount of memory needed to store the elements of the largest
        Jacobian matrix during the process of estimating the gradient-boosted
        equivalent sources coefficients, using a double precision floating
        point for each (64 bits).
        (b) Root-mean square errors obtained after the K-Fold cross-validation
        for each pair of damping and depth parameters. The orange
        square highlights the minimum RMS value.
        (c) Root-mean square error of the residue after each iteration of the
        coefficients estimation process.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

@@

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residue after each iteration of the gradient-boosting algorithm, exposing how
to algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix vs different window sizes. Each memory requirement corresponds
        to the ammount of memory needed to store the elements of the largest
        Jacobian matrix during the process of estimating the gradient-boosted
        equivalent sources coefficients, using a double precision floating
        point for each (64 bits).
        (b) Root-mean square errors obtained after the K-Fold cross-validation
        for each pair of damping and depth parameters. The orange
        square highlights the minimum RMS value.
        (c) Root-mean square error of the residuals after each iteration of the
        coefficients estimation process.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

@@

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residuals after each iteration of the gradient-boosting algorithm, exposing how
to algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.
